---
title: "Categorical Data Tests"
author: "Mehmet ÇAY"
date: '2022-08-20'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Categorical Data Tests

Dataset is a survey. It is About mental health.

## Binom Test
```{r}
survey <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/survey.csv")

question1 <- survey$treatment

q1 <- question1[question1=="Yes"]
q2 <- append(q1, question1[question1=="No"]) 

table(q2)
```
```{r}
binom.test(x=637,n=1259,p=0.5)
```
P-Value is greater than .05, so Ho is true, half of the people took treatment in 95 percent confidence interval.

## Chi-Square Goodness of Fit Test

It is almost same with Binom test, only differences it is used when there are more than 2 category.

```{r}
work_interfere <- survey$work_interfere
table(work_interfere)

result <- chisq.test(table(work_interfere))
result$expected
result$observed
result$p.value
```
We can see what we expect and what we observe. P-value says observed values are not similar to expected values.

## Chi-Square Test of Independence



```{r}
data <- data.frame(x=survey$remote_work,y=survey$seek_help)
tbl <- table(data)

prop.table(table(data)) #table of probability

chisq.test(tbl)
```
Ho: Groups are independents. There is no relations.
P-value is greater than .05, so Ho is true. Therefore, there is no relationship between seeking help and working remote.

## Fisher Exact Test

It is used when any cell in the table is lower than 5.
```{r}
data2 <- data.frame(x=survey$treatment,y=survey$tech_company)
tbl2 <- table(data2)

fisher.test(tbl2)
```

Ho is true, odds ratio is equal to 1(95 percent confidence interval). So there is no relationship between working tech company and taking treatment.

## McNemar's Test

It is same with Fisher Exact Test but is used when we have two category and before-after situation(dependent).
```{r}

mydata <- data.frame(
          once = c('yes','yes','yes','yes','no','no'),
          sonra = c('no','yes','yes','no','no','no')
)

mcnemar.test(table(mydata))
```
Ho: There is no change. Ho is true. There is no change between before and after.
