---
title: "Correlation"
author: "Mehmet ÇAY"
date: '2022-08-20'
output: 
  html_document: 
    highlight: zenburn
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Correlation

### Pearson Correlation Test

It is used when datasets are normal.
```{r}
shapiro.test(iris$Sepal.Width)
shapiro.test(iris$Petal.Width)
shapiro.test(iris$Sepal.Length)

hist(iris$Sepal.Width)
hist(iris$Sepal.Length)

cor(iris$Sepal.Width , iris$Sepal.Length , method = "pearson")

cor.test(iris$Sepal.Width , iris$Sepal.Length , method = "pearson")

```
Result say there is relation but it is very low(-0.11).

### Kendall Rank Correlation

It is non-parametric test for correlation. It can be used continuous and ordinal variables.
```{r}
hist(iris$Petal.Width)
hist(iris$Petal.Length)

cor.test(iris$Petal.Width , iris$Petal.Length , method = "kendall")
```

Result says there is very powerful relation those varables.

### Spearman's Correlation Test

It is non-parametic test but is used in ordinal variables.

```{r}

x <-  c(2,3,4,1,1,3,4,5,1,2,2,3)
y <-  c(3,4,4,2,1,2,5,3,1,3,3,2)

cor.test(x , y , method = "spearman" )

```
Result says there is relation(0.69).

## Covariances

Shows how two variables change together.
```{r}
cov(iris$Sepal.Length , iris$Sepal.Width)
cov(iris$Petal.Length , iris$Petal.Width)
```

