---
title: "Dependent Two-Sample T-test"
author: "Mehmet ÇAY"
date: '2022-08-19'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dependent Two-Sample T-test

This test is used to compare mean of two dependent groups. Dependent groups means subject of one group provide data for another group.
Also groups must be normal distrubution.

```{r}
InsPost <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/InsPostComparison.csv")

RandomPosts <- InsPost$RPostsDuration
RelatedPosts <- InsPost$LPostsDuration
duration <- c(RandomPosts,RelatedPosts)
groups <- c(rep("Random",50),rep("Liked",50))
df <- data.frame("duration" = duration,"groups"=groups)
View(df)

shapiro.test(df$duration[df$groups=="Random"])
shapiro.test(df$duration[df$groups=="Liked"])

```

Dataset defines instagram post duration that belongs related posts and random posts. Both groups data are normal.

```{r}
bartlett.test(df$duration ~ df$groups)
```
P-Value is greater than .05, it means differences homogenity of variances equal to 0. 
Bartlett homogeneity test is used to understand variances homogeneity on normal continuity datasets.

```{r}
t.test(df$duration ~ df$groups , mu = 0 , paired = T)
```
P-value is lower than .05, so there is a significant difference between datasets. Differencces is not equal to 0. Test says mean differences %95 confidence interval is 4.7534.
So, it can be said that there is truly differences when someone sees random or related posts.
