---
title: "Independent 2-Sample T-test"
author: "Mehmet ÇAY"
date: '2022-08-19'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Independent 2-Sample T-test

It is the comparison of the mean of the observations of two continuous and normally distributed sub-samples (homogeneous variance should be approximately the same) with each other.

```{r}
df <- subset(iris , subset = (Species != "virginica"))
df$Species <- as.character(df$Species)
par(mfrow = c(1,2))
hist(df$Sepal.Width[df$Species == "setosa"])
hist(df$Sepal.Width[df$Species == "versicolor"])

```
Datasets show us the sepal width of iris according to species. What we are going to do is compare the sepal width values by species.
```{r}
shapiro.test(df$Sepal.Width[df$Species == "setosa"])
shapiro.test(df$Sepal.Width[df$Species == "versicolor"])

bartlett.test(df$Sepal.Width ~ df$Species)
```
Shapiro-Wilk test says data is normal. Bartlett homogeneity test says there exists variances homogenity. Our dataset is suitable for Independent 2-Sample T-test.
```{r}
t.test(df$Sepal.Width ~ df$Species , mu = 0 , var.equal = TRUE  )
```
P-value is much lower than .05. It means there exists significant differences between values of sepal width those two species. Test says average differences between groups is 0.519895 - 0.796105 in %95 confidence interval.
