---
title: "Kruskel Wallis"
author: "Mehmet ÇAY"
date: '2022-08-20'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Kruskel Wallis

Kruskal Wallis is a non-parametic test. It is basically ANOVA for nan-parametic independents datasets.

```{r}
library(tidyverse)

heart <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/heart.csv")

heart %>% group_by(cp) %>% summarise(Normality = shapiro.test(oldpeak)$p.value)
bartlett.test(heart$oldpeak ~ heart$cp)
```
Oldpeak is sort of medicine term. Values are not normal and homogeneity also. They are suitable for Kruskal Wallis Test.
```{r}
kruskal.test(x=heart$oldpeak,g=as.factor(heart$cp))
```

# Dunn's Test
Result says there is a significant differences at least one group. Let's do Dunn's test in order to find which group is different. It is sort of Post Hoc.
```{r}
library(dunn.test)

dunn.test(x=heart$oldpeak,g=heart$cp)
```
Results say all groups(except 0 and 3) are different significantly.

```{r}
dunn.test(x=heart$oldpeak,g=heart$cp,method="bonferroni")
```
Bonferroni methods verified our interpretation.
