---
title: "MANOVA"
author: "Mehmet ÇAY"
date: '2022-08-20'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MANOVA

Manova is kind of ANOVA but only one differences, there are more than one dependent variable. Our dependent variables will be chol and thalach.

```{r}
library(tidyverse)
library(rstatix)
library(mvnormtest)

heart <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/heart.csv")

heart %>% group_by(cp) %>% summarise(Shapiro = mshapiro_test(cbind(chol,thalach))$p.value)

identify_outliers(heart["chol"])
identify_outliers(heart["thalach"])
quantile(heart$thalach)

heart <- heart %>% filter( chol < 394 & thalach > 71)

heart %>% group_by(cp) %>% summarise(Shapiro = mshapiro_test(cbind(chol,thalach))$p.value)
```
Dataset and variables are arranged in order to do test.

```{r}
library(heplots)

bartlettTests(y=heart[c("chol","thalach")],group = heart$cp)
leveneTests(y = heart[c("chol" , "thalach")] , group = heart$cp )
```
Both Bartlett and Levene verify homogenity of variances.

```{r}
box_m(heart[c("chol" , "thalach")] , group = heart$cp)
```

P-Value is greater than .05, so Ho is true, covariances matrices are similar.
So we can apply MANOVA.
```{r}
manova <- manova(cbind(chol,thalach)~ cp, data=heart)
summary(manova)
```
H-alternative is true. There are differences between groups.

## Post Hoc

In order to find which group is different , we need to do Post Hoc test.

```{r}
grouped_heart <- heart %>% gather(key="variable",value="value",thalach , chol) %>% group_by(variable)

```
### Welch Anova Test
```{r}
grouped_heart %>% convert_as_factor(cp) %>% welch_anova_test(value ~ cp)
```
Cholesterol does not get affected by cp but thalach gets affected by cp.

### TukeyHSD Test
```{r}
grouped_heart %>% convert_as_factor(cp) %>% 
                tukey_hsd(value ~ cp)
```
TukeyHSD verifies our results.

### Games-Howell Test
```{r}
grouped_heart %>% convert_as_factor(cp) %>% 
            games_howell_test(value ~ cp)
```
Games-Howell verifies our results.
