---
title: "Normality Tests"
author: "Mehmet ÇAY"
date: '2022-08-17'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document created to show normality tests.

# Shapiro-Wilk Test

Shapiro-Wilk Test is used to understand whether dataset is normal or not. We are going to choose random 5000 elements because Shapiro-Wilk test can only test 3-5000 variables.

```{r}
library(tidyverse)
Movies <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/Movies.csv")

data <- Movies %>% select(popularity)
set.seed(920)
Index <- sample(1:nrow(data),size=5000)
smallData <- data[Index,]
hist(smallData)
```

We can see that the data is not normal. However, we need to test it to understand better, despite everything is clear in this dataset.

```{r}
shapiro.test(smallData)
```

We chose first 5000 rows , p-value(=2.2e-16) is much smaller than 0.05, so Ho is false, data is not normal.

# Kolmogorov-Smirnov Normality Test

If we had a dataset that has element smaller than 30, we need to do Kolmogorov-Smirnov Test because Shapiro-Wilk test can show us wrong result.

```{r}
dataset <- iris[1:25,]
nrow(dataset)
hist(dataset$Sepal.Length)
ks.test(dataset$Sepal.Length,pnorm)
```

In the graph it almost seems normal but again we can not be sure exactly. Test reults says p-value(=2.2e-16) is smaller than 0.05, so Ho is wrong, data is not normal.
