---
title: "T-Test"
author: "Mehmet ÇAY"
date: '2022-08-17'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# T-Test

Students' T-test or T-Test measure whether mean of dataset is different value that is given or not.
```{r}

Heights <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/Height of Male and Female by Country 2022.csv")

shapiro.test(Heights$Male.Height.in.Cm)

set.seed(115)
sample <- sample(Heights$Male.Height.in.Cm, size=100)
shapiro.test(sample)
t.test(sample,mu=180)
```
First we do T-Test on normal data. That's why we did shapiro test twice(be sure exactly).Data shows mean heights of males and females according to countries. We took a sample from dataset. P-Value(<2.2e-16) means mean is not 180 cm in %95 confidence interval.
Test showed us in 95 percent confidence interval mean is 173.0641 (172.1012 - 174.0270).
So let's try again.
```{r}
t.test(sample,mu=173)
```
And p-value is now 0.1577 which is greater than 0.8952. That means Ho is true, in 95 probability our mean is 173 cm.