---
title: "Wilcoxon Rank Sums Test"
author: "Mehmet ÇAY"
date: '2022-08-19'
output: 
  html_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Wilcoxon Rank Sums Test

Compares the shift of locations in non-normally distributed data. Basically it is used in non-normal distribution and it is a nonparametric alternative to the two sample t-test.
```{r}
weatherAUS <- read.csv("C:/Users/Mehmet ÇAY/Desktop/R/Hypothesis_Tests/weatherAUS.csv")

Albury <- data.frame(weatherAUS$Temp9am[weatherAUS$Location=="Albury"])
Albury <- Albury[1:2988,]
Cobar <- data.frame(weatherAUS$Temp9am[weatherAUS$Location=="Cobar"])
Cobar <- Cobar[1:2988,]
df <- c(Albury,Cobar)
groups <- c(rep("Albury",2988),rep("Cobar",2988))

shapiro.test(Albury)
shapiro.test(Cobar)

data <- data.frame("Temp"=df,"groups"=groups)
```
Dataset show us weather values in Australia's cities. What we are going to do is compare two cities temperature values at 9 am. Datas are not both normal which means they are suitable for test.
```{r}
wilcox.test(data$Temp ~ data$groups,mu=0)
```
P-value is much lower than .05, so differences is not equal to 0. These two cities have different temperature 9 am.
